### 2014-08-27 SP_simul.Rmd
add spatial pattern simulations

```{r setup, eval=T }

@@

# Set the location of the binary 
#
mfBin <- "~/Dropbox/cpp/SpatialAnalysis/mfsba" # /mfSBA /multiSpeciesSBA
pmBin <- "~/Dropbox/cpp/SpatialAnalysis/p-model/pmodel"

@@

# Banded pattern 64 species 256 side

@@

spa <- genUniformSAD_image(64,256)
plot_sed_image(spa,"Banded 64sp")
save_matrix_as_sed(spa,"band64_256.sed")

Dq1<- calcDq_multiSBA("band64_256.sed","q.sed 4 512 20 S",mfBin,T)
Dq1$Type <- "SRS"
hist(Dq1$R)

spa <- matrix(sample(spa),nrow=256)
save_matrix_as_sed(spa,"band64_256rnz.sed")

Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 4 512 20 S",mfBin,T)
Dq2$Type <- "rnzSRS"
Dq1<- rbind(Dq1,Dq2)
plotDq(Dq1,"Type")

ggplot(Dq1, aes(x=R.Dq,fill=Type)) + geom_density(alpha=0.2)

plot_sed_image(spa,"Randomized 64sp")

Dq2<- calcDq_multiSBA("band64_256.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "dqSAD"
Dq3<- Dq2
plotDq(Dq3,"Type")

Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

plotDqFit("t.band64_256rnz.sed","q.sed")

# Analizing this last it means that the scaling is broken at side 16
#

Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 16 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD16"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 2 16 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD2-16"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

ggplot(Dq3, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2,binwidth = 0.1,position="identity")
# copy pomExp.lin to pomac.lin
#system("cp pomExp.lin pomac.lin")

# make simulations
#if(simul) system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)

@@

spa <- genUniformSAD_image(64,512)
plot_sed_image(spa,"Banded 64sp")
save_matrix_as_sed(spa,"band64_512.sed")

Dq1<- calcDq_multiSBA("band64_512.sed","q.sed 4 512 20 S",mfBin,T)
Dq1$Type <- "SRS"

spa <- matrix(sample(spa),nrow=512)
save_matrix_as_sed(spa,"band64_512rnz.sed")

Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 4 512 20 S",mfBin,T)
Dq2$Type <- "rnzSRS"
Dq1<- rbind(Dq1,Dq2)
plotDq(Dq1,"Type")

ggplot(Dq1, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2)

plot_sed_image(spa,"Randomized 64sp")

Dq2<- calcDq_multiSBA("band64_512.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "dqSAD"
Dq3<- Dq2

Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

plotDqFit("t.band64_512rnz.sed","q.sed")

# Analizing this last it means that the scaling is broken at side 16
#

Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 16 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD16-512"
Dq3<- rbind(Dq3,Dq2)

Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 2 16 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD2-16"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

ggplot(Dq3, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2,binwidth = 0.1,position="identity")

@@

Thus DqSAD works in the range 2-16

# Now simulate an image with logseries SAD for 64 species

* Discrete bands?
* Random

```{r simul_ls_512, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

# Generate an image following a logseries distribution with 64 sp 
# an regular spatial distribution
spa <- genFisherSAD_image(64,512)

plot_sed_image(spa,"Regular Fisher  64sp",0,64,10)
save_matrix_as_sed(spa,"fish64_512.sed")

Dq1<- calcDq_multiSBA("fish64_512.sed","q.sed 4 512 20 S",mfBin,T)
Dq1$Type <- "SRS"

# 
spa <- matrix(sample(spa),nrow=512)
save_matrix_as_sed(spa,"fisher64_512rnz.sed")
plot_sed_image(spa,"Rnz Fisher  64sp",0,64,5)

Dq2<- calcDq_multiSBA("fisher64_512rnz.sed","q.sed 4 512 20 S",mfBin,T)
Dq2$Type <- "rnzSRS"
Dq1<- rbind(Dq1,Dq2)
plotDq(Dq1,"Type")

ggplot(Dq1, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2)

# Ahora con SAD

Dq3<- calcDq_multiSBA("fish64_512.sed","q.sed 4 512 20 E",mfBin,T)
Dq3$Type <- "DqSAD"
#Dq3<- rbind(Dq3,Dq2)

Dq2<- calcDq_multiSBA("fisher64_512rnz.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD"
Dq3<- rbind(Dq3,Dq2)

plotDq(Dq3,"Type")

ggplot(Dq3, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2)
Dq3[Dq3$R.Dq<0.6,]
setwd(oldcd)
```

>>>>

```{r setup, eval=T }
load(".RData")

@@

# Set the location of the binary 
#
mfBin <- "~/Dropbox/cpp/SpatialAnalysis/mfsba" # /mfSBA /multiSpeciesSBA

@@

# Banded pattern of species with uniform  SAD 256 side

@@

DqF <- compMethods_UniformSAD(8,256)

DqF <- rbind(DqF,compMethods_UniformSAD(64,256))

DqF <- rbind(DqF,compMethods_UniformSAD(256,256))

# Analizing this last it means that the scaling is broken at side 16
#  
#Dq2<- calcDq_multiSBA(fname1,"q.sed 16 1024 20 E",mfBin,T)
#Dq2$Type <- "rnzDqSAD16-512"
#Dq3<- rbind(Dq3,Dq2)
#
##Dq2<- calcDq_multiSBA(fname1,"q.sed 2 16 20 E",mfBin,T)
#Dq2$Type <- "rnzDqSAD2-16"
#Dq3<- rbind(Dq3,Dq2)
#plotDq(Dq3,"Type")

pandoc.table(DqF[DqF$R.Dq<0.8,],caption="R2<0.8")
setwd(oldcd)
```

@@

DqF <- rbind(DqF,compMethods_UniformSAD(64,512))

@@

Thus DqSAD works in the range 2-8 2-16 2-32 depending on the number of species

# Now simulate an image with logseries SAD with 8, 64 & 256 species

# Test logseries SAD side = 256

```{r simul_ls_256, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

DqF <- rbind(DqF,compMethods_FisherSAD(8,256))

DqF <- rbind(DqF,compMethods_FisherSAD(64,256))

DqF <- rbind(DqF,compMethods_FisherSAD(256,256))

setwd(oldcd)

# Test logseries SAD side=512

```{r simul_ls_512b, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

DqF <- rbind(DqF,compMethods_FisherSAD(8,512,F))

DqF <- rbind(DqF,compMethods_FisherSAD(64,512,F))

DqF <- rbind(DqF,compMethods_FisherSAD(256,512,F))

setwd(oldcd)
rm(Dq1,Dq2,spa)

# Simulate with logseries and the neutral model

```{r simul_neu_256, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

DqF <- rbind(DqF,compMethods_NeutralSAD(8,256,T))

DqF <- rbind(DqF,compMethods_NeutralSAD(64,256,T))

DqF <- rbind(DqF,compMethods_NeutralSAD(256,256,T))
setwd(oldcd)
rm(nsp,side,spa)
save.image()
